Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\paragraph{Methods}

To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
Multiple linear regrssion is a continuation of simple linear regression. 
For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
The general form of the multiple linear regression model is as follows:

@@

In this equation, Y is an outcomes that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
$\beta_n X_n$ is the last regression coefficent for the final variable in the model.
$\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.

>>>>

\paragraph{Methods} 
To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
Multiple linear regrssion is a continuation of simple linear regression. 
For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
The general form of the multiple linear regression model is as follows:

@@

In this equation, Y is an outcome that is a continuous measurement. $\beta_0$ is the intercept, $\beta_1 X_1$ is the regression coefficent of the first independent variable. 
$\beta_n X_n$ is the last regression coefficent for the final variable in the model.
$\epsilon$ represents how much variation there is in our estimate for the dependent variable, or otherwise known as model error.

For this research, the data will be split into two datasets, a training set and a validation set. 
This procedure is used to measure the performance of the models built. 
The training dataset is used to fit the desired model, whereas the validation dataset is used to evaluate the fit of that desired model. 
For this purpose, the data will be split into .8 train and .2 into validation.
